Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
Intro

​\Section{Introduction}
Coping with change in the software development domain is difficult at best, it is further exasperated by trying to apply changes that do not mesh well with existing development paradigms. How then, do large companies, especially those utilising multiple development paradigms, cope with this kind of change?

Paradigms in this context will be considered to be those which relate to software development. For example, we would consider Model Driven Software Development to be a development paradigm. In this study we use the term manual coding to describe development without the use of any particular paradigm. The difference being that MDSD is heavily focused upon models and a high level of abstraction for the design of code, whereas manual coding is a standard development process. Our definition of change is not limited to the aforementioned examples, we would consider any changes to development paradigms such as a company wishing to implement processes such as Scrum or introducing Test Driven Development.

>>>>

​\Section{Introduction}
Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs. The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML). The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code.

The benefits of MDSD have consistently been reported in academia. Many large companies such as Ericsson and Volvo also use MDSD as a part of their development chain. In industry, however, MDSD struggles to make a (full) (x-wide) (XXX) breakthrough and it is mostly used for niche systems such as embedded and safety-critical systems.
